---
title: "TestCycleData3"
output: md_document
date: '2022-06-24'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(remotes)
library(rmarkdown)
library(skimr)
library(sf)
library(pct)
library(stats19)
library(tidyverse)
library(tmap)
library(tmaptools)
library(knitr)
```

```{r}
tmap_mode("view")
```

```{r}
cycle_trips = get_pct_rnet(region="south-yorkshire")
zones= get_pct_zones("south-yorkshire")
```

```{r results='asis'}
View(cycle_trips)
```
## Number of cycle trips made on the current road network
```{r}
cycle_trips %>%
  select(bicycle) %>% 
  plot()
```

##South Yorkshire Regions

```{r}
zones %>% 
  select(lad_name) %>% 
  plot()
```

## LSOA regions within Sheffield

```{r}
zones_sheffield = zones%>% 
  filter(lad_name == "Sheffield") %>%
  select(lad11cd) %>%
  plot(color = "deepskyblue", fill= NA, main= "Sheffield")
```

```{r}
zones_sheffield2 = zones %>% 
  filter(lad_name == "Sheffield")
```

```{r}
rnet_sheffield = cycle_trips[zones_sheffield2, ]
```

## Cycle trips in Sheffield

```{r}
rnet_sheffield %>%
   select(bicycle) %>%
  plot(key.pos=1) 
```


## Cycle trips under the gender equality scenario

```{r}
rnet_sheffield %>%
  select(gendereq_slc) %>%
  plot(key.pos=1)
```

## Cycle trips under the Dutch scenario

```{r}
rnet_sheffield %>%
  select(dutch_slc) %>%
  plot(key.pos=1)
```




```{r}
View(pct_regions_lookup)
```


```{r}
desire = get_pct_lines(region = "south-yorkshire")
```

```{r}
View(desire)
```

## Desire lines for the Dutch scenario (whole of South Yorkshire)

```{r}
plot(desire["dutch_slc"])
```


```{r}
desire_sheffield = desire %>%
   filter(lad_name1 == "Sheffield")
```

```{r}
plot(desire_sheffield)
```

```{r}
View(desire_sheffield)
```

## Cycle desire lines for Sheffield

```{r}
plot(desire_sheffield["bicycle"], key.pos=1,)
```

## Current potential number of cycle journeys under the current scenario and current network

```{r}
rnet_sheffield %>%
  tm_shape() +
  tm_lines(col= "blueviolet", lwd = "bicycle", scale = 9)
```
```{r}
tmap_mode("plot")
```
 
```{r}
rnet_sheffield %>%
  tm_shape() +
  tm_lines(col= "red", lwd = "ebike_slc", scale = 9)
```


```{r}
extra_tags= c("maxspeed", "bicycle", "bus")
osm_data_region = osmextract::oe_get_network("south yorkshire", mode = "cycling", extra_tags = extra_tags)
```
```{r}
osm_sheffield = osm_data_region[zones_sheffield2, ]
```

```{r}
osm_sheffield %>%
  sf::st_drop_geometry() %>%
  skimr::skim()
```

```{r}
osm_cycleways = osm_sheffield %>%
  filter(highway == "cycleway")
```

```{r}
qtm(osm_cycleways)
```

```{r}
osm_speed = osm_sheffield %>%
  select(maxspeed)
```

```{r}
plot(osm_speed, key.pos = 1, lwd = "maxspeed",)
```

```{r}
osm_sheffield %>%
  tm_shape() +
  tm_lines("maxspeed")
```

```{r}
qtm(osm_speed)
```

